Efficient Coalition Formation for Web Services

### 2013-03-08 papers/coalition/coalition.tex
Changes

In coalition-formation games, formation of the coalitions is the most important aspect of in the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer not having a centralized decision maker dictating all web services their decisions. Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions. 
This merge-and-split algorithm is designed to be adoptable for different problems. It two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition. Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$. For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services). In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff. ($p_i \geq q_i$ with at least one element $p_i > q_i$). As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function. More details of this algorithm and analyses of generic solutions on these types of games are described in \cite{DBLP:journals/igtr/AptW09}.

@@

Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.

>>>>

In coalition-formation games, formation of the coalitions is the most important aspect of in the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer not having a centralized decision maker dictating all web services their decisions. Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions. 
This merge-and-split algorithm is designed to be adoptable for different problems. It two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition. Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$. For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services). In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff. ($p_i \geq q_i$ with at least one element $p_i > q_i$). As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function. More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.

@@

Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.
